Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
Update on Overleaf.

\subsection{Data-Driven Performance Engineering}
\subsubsection{Sparse-Sparse Matrix Multiply (SpGEMM)}
\changwan{
Explain what is SpGEMM. why SpGEMM hard? (not sure)
three approaches. Asym time complexity?
}

@@

Figure~\cite{graph_result} (a) \changwan{add (a) in fig} shows BFS speedup over Graphs.jl, a BFS implementation with push traversal of Julia. `finch\_push\_only` only uses push traversal, whereas `finch\_push\_pull` applies direction-optimization used in GraphBLAS. As shown in Figure~\cite{graph_result} (a), direction-optimization significantly improves the performance for scale-free graphs.

>>>>

\subsection{Data-Driven Performance Engineering}
\subsubsection{Sparse-Sparse Matrix Multiply (SpGEMM)}
%\changwan{
%Explain what is SpGEMM. why SpGEMM hard? (not sure)
%three approaches. Asym time complexity?
%}

@@

Figure~\cite{graph_result} (a) \changwan{add (a) in fig} shows BFS speedup over Graphs.jl, a BFS implementation with push traversal of Julia. `finch\_push\_only` only uses push traversal, whereas `finch\_push\_pull` applies direction-optimization used in GraphBLAS. Finch supports push/pull traversal, early break, so it supports direction-optimization. Finch additionaly supports the different loop orders and multiple outputs, which also improves the performance. As shown in Figure~\cite{graph_result} (a), direction-optimization significantly improves the performance for scale-free graphs. \changwan{how much average speedup?} GraphBLAS sometimes better than Finch since GraphBLAS incorporates all hardwired optimizations. We believe we will achieve a better performance if we incorporate those optimizations.
